Meta-analysis of fungicide application timing experiments for powdery mildew management

### 2020-03-01 06_Publication_wireframe_and_7_Questions.Rmd
editing and writing, and referencing

Treatment of powdery mildew in mungbean with fungicide is currently an effective method for reducing the impact of the disease. 
Past field trials in eastern Australia have trialed a range of fungicides, some of which have been registered with the APVMA (Australian Pes.....) for treating powdery mildew in mungbean [@Kelly2017a; insert all published trials here].

@@

>>>>

If the planting date is not suficiently early to avoid conducive conditions for powdery mildew, treating mungbean with fungicide is currently the next best method for reducing mungbean yield damage caused by the disease. 
Past field trials in eastern Australia have trialed a range of fungicide active ingredients (table), while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016]. 
Early trials indicated to obtain maximum efficacy a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary []. 
Some of the trialed fungicides have been registered with the APVMA [@APVMA] for treating powdery mildew in mungbean [@Kelly2017a; insert all published trials here].

@@

The data for this study was obtained from through personal correspondance with collegues and collaborating institutions.
Prior to 2012 experimental trials were undertaken by Malcolmn Riley and Dr Sue Thompson with The Department of Agriculture and Primary industres. 
Trials undertaken in 2013 were conducted by the Northern growers alliance [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
